Forecasting the 2024 US Presidential Election

### 2024-11-04 paper/paper.qmd
Updated introduction section and pdf file

The remainder of this paper is structured as follows: @sec-data details the data and measurement process; @sec-results covers model development and results; @sec-discussion discusses implications and future steps.

>>>>

The remainder of this paper is structured as follows: @sec-data details the data and measurement process; @sec-model covers the model; @sec-results provides results; and @sec-discussion discusses implications and future steps.
